Approximation as Differentiation

### 2025-07-10 main/conclusion.tex
Moving unused Agda files to .
Just use + for binary coprod
laird07, fix ref.

2. Conjecture that the category with $(X : Cpo, \partial X : X \to \CLatGal)$, where $\CLatGal$ is the category of complete lattices and galois connections is the right setting. Would need to investigate the connections with dI-domains, bidomains, and bistable bidomains (Laird).

@@

Would be better to have an implementation that worked by translation,
instead of interpreting directly as Agda functions. See work by
Smeding and Vákár on translations. To formalise this, we'd need
to... See also $\Fam(\PSh_{\CMon}(Syn))$?

>>>>

2. Conjecture that the category with $(X : \namedcat{Cpo}, \partial X : X \to \CLatGal)$, where $\CLatGal$ is the category of complete lattices and galois connections is the right setting. Would need to investigate the connections with dI-domains, bidomains, and bistable bidomains (\cite{laird07}).

@@

Would be better to have an implementation that worked by translation,
instead of interpreting directly as Agda functions. See work by
Smeding and Vákár on translations. To formalise this, we'd need
to... See also $\Fam(\PSh_{\CMon}(\namedcat{Syn}))$?
